Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-04-05 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: missing k subs

Let us now establish the connection between theory-agnostic framework of the
$\pSEOB$ waveform model and the theory-specific QNM calculations.
%
We begin by rewriting $\omega_{k}$ and $\tau_{k}$, given by Eqs.~\eqref{eq:kerr_expansion} as,
%
\begin{subequations}
\label{eq:qnm_nongr_iso}
\begin{align}
M \omega_{k} &= \gamma \left( \delta\omega^{(0)} \omega^{(0)} + \chi \delta\omega^{(1)} \omega^{(1)} \right)
+ \sum_{n=0}^{N_{\rm max}} \chi^{n} \omega^{(n)}\,,
\\
\tau_{k}/M   &= \gamma \left( \delta\tau^{(0)} \tau^{(0)} + \chi \delta\tau^{(1)} \tau^{(1)} \right)
+ \sum_{n=0}^{N_{\rm max}} \chi^{n} \tau^{(n)}\,,
\end{align}
\end{subequations}
%
We will work exclusively with the $\ell = m = 2$ and $n = 0$ (fundamental mode)
QNM, i.e., $k = \{2,\, 2,\, 0\}$. For this reason we will omit the subcripts
$k$ hereafter and no ambiguity in notation between the overtone index and the
subscript $n$ in the series should arise.
%
We have also pulled out from the sum all beyond-GR corrections, restricting
ourselves to the nonspinning ($n=0$) and linear-order in spin ($n=1$)
corrections to the Kerr QNMs.
%
% These corrections are encoded in the coefficients $\delta\omega^{(n)}$ and $\delta\tau^{(n)}$.

@@

In this theory, we considered only $N_{\rm max} = 0$. We found that the
inclusion of the spin corrections yields waveforms which for $\ell_{\rm qEFT} \gtrsim 80$~km
for which the ringdown portions of the larger than the inspiral-plunge part \dots
%
To avoid this issue we lowered the value of $\ell^{\rm max}_{\rm qEFT}$, but by doing so we obtained posteriors
which were essentially uniform. Thus, we do not quote any results for $N_{\rm max} = 1$.
%
Table~\ref{tab:summary_qeft} summarizes our findings for the quartic EFT of GR.
%
\hs{Discuss. I don't have a good argument for why the $N_{\rm max} = 1$ are breaking down other than
we just fail to compute the waveform for $\ell_{\rm qEFT} = 80~$~km for GW150914-like masses.}

>>>>

Let us now establish the connection between theory-agnostic framework of the
$\pSEOB$ waveform model and the theory-specific QNM calculations.
%
We begin by rewriting $\omega_{k}$ and $\tau_{k}$, given by Eqs.~\eqref{eq:kerr_expansion} as,
%
\begin{subequations}
\label{eq:qnm_nongr_iso}
\begin{align}
    M \omega_{k} &= \gamma \left( \delta\omega^{(0)}_{k} \omega^{(0)}_{k} + \chi \delta\omega^{(1)}_{k} \omega^{(1)}_{k} \right)
    + \sum_{n=0}^{N_{\rm max}} \chi^{n} \omega^{(n)}_{k} \,,
\\
    \tau_{k}/M   &= \gamma \left( \delta\tau^{(0)}_{k} \tau^{(0)}_{k} + \chi \delta\tau^{(1)}_{k} \tau^{(1)}_{k} \right)
    + \sum_{n=0}^{N_{\rm max}} \chi^{n} \tau^{(n)}_{k}\,,
\end{align}
\end{subequations}
%
We will work exclusively with the $\ell = m = 2$ and $n = 0$ (fundamental mode)
QNM, i.e., $k = \{2,\, 2,\, 0\}$. For this reason we will omit the subcripts
$k$ hereafter and no ambiguity in notation between the overtone index and the
subscript $n$ in the series should arise.
%
We have also pulled out from the sum all beyond-GR corrections, restricting
ourselves to the nonspinning ($n=0$) and linear-order in spin ($n=1$)
corrections to the Kerr QNMs.
%
% These corrections are encoded in the coefficients $\delta\omega^{(n)}$ and $\delta\tau^{(n)}$.

@@

In this theory, we considered only $N_{\rm max} = 0$. We found that the
inclusion of the spin corrections yields waveforms which for $\ell_{\rm qEFT} \gtrsim 80$~km
for which the ringdown portions of the larger than the inspiral-plunge part \dots
%
To avoid this issue we lowered the value of $\ell^{\rm max}_{\rm qEFT}$, but by doing so we obtained posteriors
which were essentially uniform. Thus, we do not quote any results for $N_{\rm max} = 1$.
%
Table~\ref{tab:summary_qeft} summarizes our findings for the quartic EFT of GR.
%
\hs{Discuss. I don't have a good argument for why the $N_{\rm max} = 1$ simulations are breaking down other than
we just fail to compute the waveform for $\ell_{\rm qEFT} = 80~$~km for GW150914-like masses.}
